
\section{Scenario Identifyng}

\subsection{Scenario 1 - Reservation}
\begin{flushleft}
Paul, a businessman, has to go to Milan by train in order to participate
to an important meeting.\\
As the office where they have to meet is 5 km far from the railway
station and taxis are too much expensive, he decides to use $\mathit{PowerEnJoy}$
from his smartphone. \\
He notices, thanks to the map on the app, that there is a parking
area next to the railway station with a lot of available cars. He
then reserves one of these electric cars so that, as soon as he arrives
there, he'll be able to reach the office very quickly and in a green
way. 
\par\end{flushleft}

\subsection{Scenario 2 - ``Two Passengers discount''}

Paul is a student that goes to Politecnico University in Milan. He
lives in a city near Milan but unfortunately train's schedule is very
prohibitive: he should wake up at 5 o'clock in the morning in order
to arrive on time at the lecture that starts at 8:00.\\
He found out about $\mathit{PowerEnJoy}$ from two of his friends
in his city that attend the same University. They decide to use together
car-sharing service so they can save money using the ``two passegners
discount''.\\
Since their city is full of electric-car, everyday they make a reservation
of a car and go to the University together.\\
In this way, not only they save money, but they are also much more
comfortable in reaching the University.

\subsection{Scenario 3 - Registration}

Paul has just learnt about $\mathit{PowerEnJoy}$.\\
This evening he has to go to dinner with his girlfriend, Sarah, so
he decides to try it. Then he downloads the app and looks for cars
near his location. He finds many cars, he's about to reserve one of
them but reservation is not permitted to guests.\\
For this reason he has to sign up: following the application instructions
he provides his personal informations, his driving license and he
specifies his payment method.\\
After that he's able to reserve the car for the special occasion.

\subsection{Scenario 4 - OPERATOR maintenance}

Jonathan is doing his periodical check of the car in his competence
area. He finds out that a dishonest user has left a car with a broken
light, without communicate that. So Jonhatan, by his maintenance service
system, makes the car unavailable and starts to solve the maintenance
problem.

\subsection{Scenario 5 - OPERATOR notification}

Amy is driving an electrical car reserved with $\mathit{PowerEnJoy}$.
As always she is very late today, and she notices that, if she wants
to arrive on time, she will not be able to bring the car at the station
where it can be charged. So she decides to park the car as close as
possible to her destination. \\
After she has parked, the OPERATOR Jonathan, receives a notification
on his maintenance service view, that tells him where Amy's car is,
and that it is almost completely discharged.\\
Now Jonathan can go take the car and make it again available for the
next customer.

\subsection{Scenario 6 - USER comunicates a malfunction to the system}

Amy is driving an electrical car reserved with $\mathit{PowerEnJoy}$.
Arrived at is destination, she starts a parking maneuver, but she
hurts a light pole, doing a damage to the vehicle. Amy is an honest
person, and following the application instruction she comunicates
to the system that she has damaged the car. The system will comunicate
to an OPERATOR about the damage.
