
\section{Overall description}

\subsection{Product perspective}

In this section the system boundaries are described. Are described
the interfaces provided by external systems that the software to be
will use to provide the required functionalities.

\subsubsection{Payment methods}

The software relies on external transactional system in order to administer
in a good way the payment process and to be able to manage exceptional
situations too (like users unavailability of money USERs). \\
So the system doesn't care about how the payments are done, but only
that the USER has provided one of the payment methods defined in the
assuption section. 

\subsubsection{Car technology}

The software to be will use the tecnologies provided by a system already
present on cars, in order to carry out the needed actions. The used
API provides a secure connection between cars and the central system
via internet, and the following commands that the central system can
impose on car:
\begin{itemize}
\item Lock: locks the car doors.
\item Unlock: unlocks the car doors.
\item Get position: the car sends to the central system its position.
\item Get status: the car sends to the central system detailed information
about his current status.
\end{itemize}

\subsubsection{Operators, maintenance, malfunctions and damanges.}

The cars availability depends heavily on the presence of a staff that
does cars maintenance. So the sotware to be relies on the presence
of the staff in order to guarantee availability of cars, and it will
provide to operators information that helps the cars maintenance.
Operators will manage damanges to cars and consequence for the responsible,
so the system will only help the OPERATORs in maintenance, and guarantee
a way to comunicate malfunction and damanges.
